%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingtwo}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% c++ symbol
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jun-Wei Liu} & Email: 1026oscar1@gmail.com\\
  \href{https://www.linkedin.com/in/junw-liu/}{linkedin/junw-liu} & Mobile: +886 933974081 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheadingtwo
      {National Taiwan University (NTU)}{Taipei, Taiwan}
      {Bachelor's degree in Computer Science and Information Engineering}{Sept. 2020 -- Jun. 2025}
      {Bachelor's degree in Sociology}{Sept. 2021 -- Jun. 2025}
      \resumeItemListStart
        \resumeItem{}{Recipient of the 2020 National Taiwan University Fu Bell Entrance Scholarships (70 out of 3758 students).}
        \resumeItem{}{Completed one-year exchange program at KTH Royal Institute of Technology in Sweden from 2022 to 2023.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience in Computer Science}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Thingnario}{Taipei, Taiwan}
      {Site Reliability Engineering Intern}{Jun. 2023 -- Aug. 2023}
      \resumeItemListStart
        \resumeItem{}{Integrated testing scripts across diverse GCP servers using the centralized scheduler/runner Cronicle, consolidating error messages into an Elasticsearch-powered database for streamlined log analysis and more effective troubleshooting.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Institutes of Sweden (RISE)}{Stockholm, Sweden}
      {Research Intern, supervised by Dr. Paris Carbone}{Apr. 2023 -- Jul. 2023}
      \resumeItemListStart
        \resumeItem{}{Dockerized and refactored the Java-based throughput assessment of machine learning models across various stream-processing frameworks (e.g., Apache Flink, Kafka Streams, and Spark Streaming) to simulate real-world performance in an industrial setting, leading to its acceptance at EDBT/ICDT 2024.}
      \resumeItemListEnd

    \resumeSubheading
      {Mobagel}{Taipei, Taiwan}
      {Software Engineer Intern}{Jun. 2022 -- Aug. 2022}
      \resumeItemListStart
        \resumeItem{}{Developed error codes for Decanter AI's AutoML Scala-based system, optimizing data processing, model training, and prediction request handling, which improved error message feedback on the web frontend.}
        \resumeItem{}{Optimized the "sanitizing" module responsible for managing special characters in file headers during user dataset uploads, enhancing data quality and user experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Sensay}{United States (Remote)}
      {Machine Learning Intern}{Jul. 2021 -- Aug. 2021}
      \resumeItemListStart
        \resumeItem{}{Enhanced automated speech assessment on Sensay's English learning platform by applying machine learning techniques from early ETS research (2008–2014), improving the scoring system based on the company’s dataset.}
        \resumeItem{}{Developed an interactive audio visualization feedback system for language learning, integrating insights from academic research on acoustic feature visualization for pronunciation training, fostering a more engaging and effective platform for students.}
      \resumeItemListEnd
    
      \resumeSubheading
        {Innoveon}{Taipei, Taiwan}
        {Deep Learning Intern}{Jul. 2020 -- Sept. 2020}
        \resumeItemListStart
          \resumeItem{}{Developed an image alignment algorithm for defect detection in racket production, incorporating techniques from four influential papers on convolutional neural networks (CNNs).}
          \resumeItem{}{Conducted experiments on data augmentation using the company’s dataset, applying feature disentanglement methods from three key papers on variational autoencoders (VAEs).}
        \resumeItemListEnd
      
        \resumeSubheading
          {Institute of Information Science, Academia Sinica}{Taipei, Taiwan}
          {High School Research Project, supervised by Dr. Li Su} {Aug. 2018 -- Jul. 2020}
          \resumeItemListStart
            \resumeItem{}{Published a first-authored paper "Body Movement Generation for Expressive Violin Performance Applying Neural Networks" in ICASSP 2020. [\href{https://ieeexplore.ieee.org/document/9054463}{IEEExplore}]}
            \resumeItem{}{Developed a neural network-based framework with Keras to generate expressive violin performance body skeletons.}
            \resumeItem{}{Conducted comprehensive subjective and objective evaluations to assess the likeness and naturalness of the generated skeletons.}
          \resumeItemListEnd
          
  \resumeSubHeadingListEnd


\section{Experience in Sociology}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Institute of European and American Studies, Academia Sinica}{Taipei, Taiwan}
      {Research Assistant, supervised by Dr. Min-Hsiung, Huang}{Apr. 2024 -- Jul. 2024}
      \resumeItemListStart
        \resumeItem{}{Analysed cross-national longitudinal datasets, such as Programme for International Student Assessment (PISA) and the Taiwan Educational Panel Survey (TEPS), to investigate educational inequality in Taiwan.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Institute of Sociology, Academia Sinica}{Taipei, Taiwan}
      {Research Assistant, supervised by Dr. Hsuan-Wei Lee}{Sept. 2021 -- Feb. 2023}
      \resumeItemListStart
        \resumeItem{}{Replicated 21 agent-based modeling papers from the sociology journals AJS and ASR using Python, ensuring rigorous reproducibility standards and enhancing the reliability of sociological research methodologies.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

\section{Activities}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {2022 \& 2023 APCS Camp}{Taipei, Taiwan}
      {$\CC$ Lecturer}{Mar. 2022 -- Jul. 2023}
      \resumeItemListStart
        \resumeItem{}{Designed teaching materials and delivered online lectures on fundamental concepts of functions and recursion in $\CC$ to 80 high school students, aiding their preparation for the Advanced Placement Computer Science (APCS) test in Taiwan.}
      \resumeItemListEnd
          
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}